This is an example of article title

### 2025-10-31 paper/paper.tex
Make code blocks floating.

\begin{figure}
    \centering
    \includegraphics[width=0.12\textwidth]{logo.png}
    \vspace{.5\baselineskip}
    \caption*{Logo of \texttt{LieGroups.jl}.}%
    \label{fig:liegroups_logo}
\end{figure}

@@

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:deCasteljauLieGroup},
    caption={de-Casteljau algorithm on a Lie group.}
]
using LieGroups, ManifoldsBase, RecursiveArrayTools
using CairoMakie
"""
    deCasteljauLieGroup(G, cp, t)

@@

\begin{figure}
    % Arrow scale factor
    \def\arrowscale{0.15}

@@

We evaluate the corresponding Bézier curves on both Lie groups using the Code~\ref{lst:bezierLieGroupExample}.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:bezierLieGroupExample},
    caption={Evaluating Bézier curves on \(\mathrm{SE}(2)\) and \(\mathrm{SO}(2) \times \mathcal T(2)\).},
    mathescape
]
SO2 = SpecialOrthogonalGroup(2)
R2 = TranslationGroup(2)
SO2xR2 = SO2 $\times$ R2
ts = range(0, 1, length=35)
q1 = [
    deCasteljauLieGroup(SO2xT2, cp, t) for t in ts
]
SE2 = SpecialEuclideanGroup(2)
q2 = [deCasteljauLieGroup(SE2, cp, t) for t in ts]
\end{lstlisting}

@@

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) where (p,θ) and (dp,dθ) are
# passed as the first argument, system parameters
# as the second one and time as the last one
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    c = [tau / sp.Icm, a...]
    ddx = hat(sp.lie_algebra, c, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}

@@

\begin{lstlisting}[
    language = Julia,
    numbers=left,
    label={lst:heun},
    caption={Step calculation for the RKMK Heun method.}
]
function integrator_step!(
        A::GroupAction, sp::SystemParameters,
        y, f, t, dt
) # The dynamics function is passed as f
    Ie = Identity(A.group)
    F1 = (dt / 2) * f(y, sp, t)
    tmp = zero_vector(A.manifold, y)
    diff_group_apply!(A, tmp, Ie, y, F1)
    y2 = exp(A.manifold, y, tmp)
    F2 = dt * f(y2, sp, t + dt/2)
    diff_group_apply!(A, tmp, Ie, y, F2)
    exp!(base_manifold(A), y, y, tmp)
end
\end{lstlisting}

\begin{figure}
    % Arrow scale factor
    \def\arrowscale{1.0}

>>>>

\begin{figure}[tbp]
    \centering
    \includegraphics[width=0.12\textwidth]{logo.png}
    \vspace{.5\baselineskip}
    \caption*{Logo of \texttt{LieGroups.jl}.}%
    \label{fig:liegroups_logo}
\end{figure}

@@

\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:deCasteljauLieGroup},
    caption={de-Casteljau algorithm on a Lie group.}
]
using LieGroups, ManifoldsBase, RecursiveArrayTools
using CairoMakie
"""
    deCasteljauLieGroup(G, cp, t)

@@

@@

We evaluate the corresponding Bézier curves on both Lie groups using the Code~\ref{lst:bezierLieGroupExample}.
\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:bezierLieGroupExample},
    caption={Evaluating Bézier curves on \(\mathrm{SE}(2)\) and \(\mathrm{SO}(2) \times \mathcal T(2)\).},
    mathescape
]
SO2 = SpecialOrthogonalGroup(2)
R2 = TranslationGroup(2)
SO2xR2 = SO2 $\times$ R2
ts = range(0, 1, length=35)
q1 = [
    deCasteljauLieGroup(SO2xT2, cp, t) for t in ts
]
SE2 = SpecialEuclideanGroup(2)
q2 = [deCasteljauLieGroup(SE2, cp, t) for t in ts]
\end{lstlisting}

\begin{figure}[tbp]
    % Arrow scale factor
    \def\arrowscale{0.15}

@@

@@

Code~\ref{lst:rod-dynamics} shows functions that calculate the right hand side of the ODE, where \lstinline{E_field} is a function that calculates electric field strength from the point charges at the given point.
The function \lstinline{force_and_torque} calculates the force and torque affecting the rod, while \lstinline{dynamics} converts them to the Lie algebra element can be used by the solver.
\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:rod-dynamics},
    caption={Dynamics of a rod affected by point charges.},
    mathescape
]
function force_and_torque(
        sp::SystemParameters, Fθ, r
    )
    u, u${}_\perp$ = eachrow(Fθ)
    F, $\tau$ = zeros(2), 0.0
    for s in range(-sp.L/2, sp.L/2; length=Nq)
        E = E_field(sp, r .+ s .* u)
        F .+= sp.$\lambda$ * E * (sp.L/(Nq-1))
        $\tau$ += sp.$\lambda$ * s * dot(u${}_\perp$, E) * (sp.L/(Nq-1))
    end
    return F, $\tau$
end
# f((p,θ), (dp,dθ), t) where (p,θ) and (dp,dθ) are
# passed as the first argument, system parameters
# as the second one and time as the last one
function dynamics(state, sp::SystemParameters, t)
    p, dp = state.x
    F, tau = force_and_torque(sp, p.x...)
    a = F ./ sp.M
    c = [tau / sp.Icm, a...]
    ddx = hat(sp.lie_algebra, c, ArrayPartition)
    return ArrayPartition(dp, ddx)
end
\end{lstlisting}

@@

\begin{lstlisting}[
    float=tbp,
    language = Julia,
    numbers=left,
    label={lst:heun},
    caption={Step calculation for the RKMK Heun method.}
]
function integrator_step!(
        A::GroupAction, sp::SystemParameters,
        y, f, t, dt
) # The dynamics function is passed as f
    Ie = Identity(A.group)
    F1 = (dt / 2) * f(y, sp, t)
    tmp = zero_vector(A.manifold, y)
    diff_group_apply!(A, tmp, Ie, y, F1)
    y2 = exp(A.manifold, y, tmp)
    F2 = dt * f(y2, sp, t + dt/2)
    diff_group_apply!(A, tmp, Ie, y, F2)
    exp!(base_manifold(A), y, y, tmp)
end
\end{lstlisting}

\begin{figure}[tbp]
    % Arrow scale factor
    \def\arrowscale{1.0}
